Details of specific functions

### 2022-01-18 inst/gitbook/03_specific-tutorials.Rmd
Manual update for v1.7 INIT

>>>>

## Disparity of variance-covariance matrices (covar) {#covar}

What is a variance-covariance matrix
How to get them: MCMCglmm @MCMCglmm from @hadfield2010 (but see also @mulTree)

### Creating a `dispRity` object with a `$covar` component

### Visualising covar objects

### Disparity analyses with a `$covar` component

`as.covar`

#### Elaborations and explorations

But see probably paper

Finally there are other tools for manipulating MCMCglmm objects. See other [MCMCglmm utilities](#MCMCglmm-utilities)
